Supporting Information: Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-02-26 paper/rebuttal/rebuttal.tex

%
% SECTION-PERFORMANCE COMPARISONS
%
\section{Performance of \textit{word2vec} compared with baselines}
\subsection{Alternatives considered}
In our original manuscript, we compared the performance of what we call the embedding distance---the cosine distance between vectors learned by \textit{word2vec}---to a range of alternatives.
These alternatives included the geographic distance between locations, the distance most commonly used in definitions of the gravity model of mobility, along with the dot product similarity between embedding vectors, and the cosine distance and Jensen-Shannon divergence between vectors obtained from a personalized-page-ranking procedure on the underlying mobility network.

Following the advice of the referees, we also add additional baselines to illustrate how the embedding distance performs compared to simpler embedding alternatives.
The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
The third baseline is the distance between vectors obtained through a Laplacian eigenmap embedding of the location of the matrix.

In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
The \textit{word2vec} model  implicitly approximates this matrix-factorization procedure, and so comparison to these ``Levy'' distances can demonstrate whether the approximation of neural embeddings outperform direct-calculations. 
Furthermore, we computed an embedding that attempts to directly-optimize for a gravity-law relationship between relations, one created using singular-vector decomposition (SVD) and another with multidimensional scaling (MDS).

@@

\subsection{New experimental parameters}
In addition to the new baselines, we have also incorporated additional experimental parameters into our analysis.
The first is $\gamma$, a hyper-parameter of the \textit{word2vec} model, which defines the exponent which shapes the negative sampling distribution.
The default of `\texttt{gensim's} implementation of \textit{word2vec} is to set $\gamma = 0.75$, and this was the value used in our original manuscript.
However, to connect \textit{word2vec} to the gravity model of mobility, we assume $\gamma = 1.0$ (see section 1).
We now report all main results using $\gamma = 1.0$, however we also compare its performance to embeddings learned using $\gamma = 0.75$, as we do with the number of embedded dimensions and window size.

We also consider an experimental parameter differentiating between definitions of \textit{population}, in the context of scientific mobility.
Our original manuscript defined the population of an organization as its average annual number of unique mobile and non-mobile authors who publish with that organizational affiliation.
However, because non-mobile authors do not have mobility trajectories, and are thus not included in training of the embedding, this definition of population introduces additional, potentially confounding information into the experiment.
To tease apart the impact of population definitions, we consider two additional definitions.
The first defines an organization's population as the average annual number of unique mobile authors, only, who publish with the organization.
The second definition defines the population akin to language, as simply its frequency across all mobility trajectories.

\subsection{Result}

%
% Figure---Metric performance
%
\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.95\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
	\mycaption
	{Neural embeddings outperform baselines for scientific mobility.}
	{
		Cosine distance between embedding vectors generated with \textit{word2vec} explains more of the flux, and better predicts flux when used in the gravity model of mobility than geographic distance and other baselines.
		Shown is the correlation between the flux and embedding distances, measured with $R^{2}$ (left), and the prediction error when using the distance as input to the gravity model of mobility.
    The asterisk denotes the top-performing metric.
		For prediction error, we show results based on both the exponential and power-law forms of the gravity model.
		All embedding-based methods use dimensions of 300.
		Here, embedding distance is obtained from neural embeddings learned with window size of 1 and $\gamma = 1$.
		In all cases, organization population is defined as the mean annualized number of unique mobile and non-mobile authors, and flux is calculated for all global mobility.
		Baselines include the top-performing distance metrics calculated between vectors obtained by personalized-page rank (PPR), singular value decomposition (SVD), laplacian eigenmap, direct-factorization following Levy's approach~\autocite{levy2014neural}, and direct optimization of the gravity model using SVD and multidimensional scaling (MDS), as well as the geographic distance between organizations.
		Embedding distance better explains and predicts flux than any other baseline, though there is some variation by experimental parameters (Table~\ref{supp:table:r2_table}, Table~\ref{supp:table:rmse_exp_table}, and Table~\ref{supp:table:rmse_power_table}).
	}
	\label{fig:supp:distancemetrics}
\end{figure}

We find that, using the best performing dimensions (300) and window size (1),  $\gamma = 1.0$, and for default experimental parameters (global mobility, population defined using all mobile and non-mobile scholars), that the embedding distance, or cosine distance between vectors learned through neural embedding, explains more of the flux, and leads to better predictions than other baselines (Fig.~\ref{fig:supp:distancemetrics}).
This performance advantage holds when considering both the exponential and the power-law forms of the gravity model of mobility.
Although the euclidean distance between directly-factorized vectors performs comparably, and even narrowly beats out the embedding distance under certain experimental conditions (Tables~\ref{supp:table:r2_table},~\ref{supp:table:rmse_exp_table},~\ref{supp:table:rmse_power_table}); \textit{word2vec} shows the msot consistent and robust performance, as suggested by Levy \& Goldberg~\autocite{levy2014neural}.
Directly-optimizing the gravity model results in comparable performance to Levy's factorization approach, narroly beating out both in prediction error for certain definitions of organization population. 
Still, the embedding distance, with its stochastic optimization algortihm reliably outperforms these directly-optimized  baselines.

@@

%
% R2 Table
%
\clearpage

\begin{landscape}

  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
  \providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}

\begin{table}[ht]
\caption{
	\textbf{Correlation between flux and distance over metrics, experimental parameters}.
	Each cell corresponds to the correlation (measured with $R^{2}$) between the real-world flux between scientific organizations, comparing the embedding distance against baseline metrics, and across subsets of mobility data and by definitions of organization population.
	The asterisk denotes the top-performing distance metric by column.
	Distance metrics are ordered from highest $R^{2}$ to lowest, based on global mobility with organization population defined using all mobile and non-mobile authors.
	``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
		population is defined in the same way for ``Mobile only'', except only using unique mobile researchers;
		``Raw freq'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding.
		Embedding distance, measured as the cosine distance between embedding vectors, explains more of the flux than baselines in nearly every case, except using raw frequency population and domestic and international mobility, where direct optimization of the gravity law works better, as well as Levy's factorization~\autocite{levy2014neural} for domestic and international only mobility.
}
\label{supp:table:r2_table}
\begin{centerbox}
\begin{threeparttable}
\small
 \setlength{\tabcolsep}{0pt}
\begin{tabular}{l l l l l l l l l l}

@@

\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{ } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Global} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{Domestic} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} \textbf{International} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}-}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.481 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.418 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.435 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.492 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.456 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.489 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.325 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.251 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.252 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity MDS euclidean} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.355 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.165 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.161 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.328 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.112 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.115 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.369 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.174 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.164 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.341 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.369 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.382 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.213 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.271 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.284 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.305 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.323 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.334 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
\arrayrulecolor{black}

### 2021-02-26 paper/current/supp.tex

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.133 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.138 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.056 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.047 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.05 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.013 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.039 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.034 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.035 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}
\end{tabular}
\end{threeparttable}\par\end{centerbox}

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding cosine} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.76 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.737 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.702 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.749 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.713 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.715 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.764 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.748 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's euclidean} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.791 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.771 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.874 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.867 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.844 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.725 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.726 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} *0.705 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Embedding dot} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.803 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.825 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.811 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.851 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.87 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.854 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.769 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.798 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.784 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

>>>>

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Gravity SVD cosine} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.122 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.118 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.133 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.138 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.056 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.047 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.05 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} \textbf{Levy's dot} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.013 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.002 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0.5}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.004 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.039 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.034 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.035 \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|>{\huxb{0, 0, 0}{0.5}}|}
\arrayrulecolor{black}
\end{tabular}
\end{threeparttable}\par\end{centerbox}

@@

@@

@@
